The Distributional Impacts of the Electricity Transition on Pollution Exposure

### 2024-12-05 MIP_Downscaled.tex

Unsurprisingly, deaths are highly correlated with CO$_2$ emissions, since both are driven by fossil-fuel combustion.  Policies that most dramatically reduce CO$_2$ emissions, also do the most to reduce aggregate deaths.
\begin{figure}
    \centering
    \includegraphics[width=1\linewidth]{Figures/Output/Deaths_vs_Emissions_GenX.png}
    \caption{Deaths are highly correlated with CO$_2$ emissions}
    \label{DeathsEmissions}
\end{figure}

>>>>

Unsurprisingly, deaths are highly correlated with CO$_2$ emissions, since both are driven by fossil-fuel combustion.  Policies that most dramatically reduce CO$_2$ emissions, also do the most to reduce aggregate deaths.
\begin{figure}
    \centering
    \includegraphics[width=1\linewidth]{Figures/Output/Deaths_vs_Emissions_withlines_GenX.png}
    \caption{Deaths are highly correlated with CO$_2$ emissions.  In this plot, points are colored by scenarios and shaped by model year.  We also draw lines to show the trajectory over time for each model.}
    \label{DeathsEmissions}
\end{figure}
